---
title: "第9章"
format: 
  html:
    theme: journal
    highlight-style: pygments
    page-layout: article
number-sections: true
toc: true
toc-depth: 3
toc-location: left
code-fold: show
date: "最終更新: `r Sys.Date()`"
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, fig.align = "left", warning = FALSE)
library(ggplot2)
library(magrittr)
library(modelsummary)
library(kableExtra)
library(CausalInferenceTextbook)
color_main <- scales::viridis_pal(option = "C")(1)
```

# [9-1, 10-1]2方向固定効果（TWFE）推定
```{r}
N <- 1000
T0 <- 4
T1 <- 6
T <- T0 + T1
```

```{r}
mean_tau_i_simul <- 0.05
sd_tau_i_simul <- 0.2

mean_tau_i_multi <- 0.1
sd_tau_i_multi <- 0.2

scale_5 <- 1
scale_6 <- -2.5
scale_7 <- -1.75
scale_8 <- -1
```

```{r}
set.seed(1)
df_design <- 
  generate_df_no_covariates(
    N = N,
    T = T,
    T0 = T0,
    mean_tau_i = mean_tau_i_simul,
    sd_tau_i = sd_tau_i_simul
  )
```

```{r}
df_design %>%
  dplyr::filter(
    z_it == 1
  ) %>% 
  dplyr::summarise(
    y = mean(tau_t)
  ) %>% 
  .[] * mean_tau_i_simul
```

```{r}
att_pop <- 
  df_design %>% 
    dplyr::filter(
      time > T0
    ) %>% 
    dplyr::pull(
      tau_t
    ) %>% 
    unique()

att_pop <- 
  mean(att_pop) * mean_tau_i_simul
```

```{r}
att_sample <- 
  df_design %>% 
  dplyr::filter(
    z_it == 1
  ) %>% 
  dplyr::summarise(
    tau_it = mean(tau_it)
  ) %>% 
  dplyr::pull(tau_it)

att_sample
```

```{r}
set.seed(1)

df_design_multiperiod <- 
  generate_df_multiperiod(
    N = N,
    T = T,
    T1 = T1,
    T0 = T0,
    diff_trend = FALSE,
    mean_tau_i = mean_tau_i_multi,
    sd_tau_i = sd_tau_i_multi,
    scale_5 = scale_5,
    scale_6 = scale_6,
    scale_7 = scale_7,
    scale_8 = scale_8
  )
```

```{r}
df_design_multiperiod %>% 
  dplyr::group_by(
    group_i
  ) %>% 
  dplyr::summarise(
    fraction = length(group_i)
  ) %>% 
  dplyr::mutate(
    fraction = fraction / sum(fraction)
  ) 
```

```{r}
mean_abs_tau_i <- 
  (
    mean_tau_i_multi + 
      sd_tau_i_multi * (
        dnorm((-mean_tau_i_multi) / sd_tau_i_multi)) / 
      (1 - pnorm((-mean_tau_i_multi) / sd_tau_i_multi))
   ) * 
    pnorm(mean_tau_i_multi / sd_tau_i_multi) -
  (
    mean_tau_i_multi -
     sd_tau_i_multi * (
        dnorm((-mean_tau_i_multi) / sd_tau_i_multi)) / 
     (pnorm((-mean_tau_i_multi) / sd_tau_i_multi))
   ) * 
    (1 - pnorm(mean_tau_i_multi / sd_tau_i_multi))
```

```{r}
att_pop_multiperiod_group <- 
  df_design_multiperiod %>% 
  dplyr::filter(
    time > T0,
    g5_i == 1
  ) %>% 
  dplyr::summarise(
    group = "5",
    att_pop_multiperiod = 
      mean(unique(tau_t)) * scale_5 * mean_abs_tau_i,
    fraction_within_group = 
      sum(z_it) / sum(df_design_multiperiod$z_it)
  )

att_pop_multiperiod_group <- 
  rbind(
    att_pop_multiperiod_group,
    df_design_multiperiod %>% 
      dplyr::filter(
        time > T0,
        g6_i == 1
      ) %>% 
      dplyr::summarise(
        group = "6",
        att_pop_multiperiod =
          mean(unique(tau_t)) * scale_6 * mean_abs_tau_i,
        fraction_within_group =
          sum(z_it) / sum(df_design_multiperiod$z_it)
      )
  )

att_pop_multiperiod_group <- 
  rbind(
    att_pop_multiperiod_group,
    df_design_multiperiod %>% 
      dplyr::filter(
        time > T0,
        g7_i == 1
      ) %>% 
      dplyr::summarise(
        group = "7",
        att_pop_multiperiod =
          mean(unique(tau_t)) * scale_7 * mean_abs_tau_i,
        fraction_within_group =
          sum(z_it) / sum(df_design_multiperiod$z_it)
      )
  )

att_pop_multiperiod_group <- 
  rbind(
    att_pop_multiperiod_group,
    df_design_multiperiod %>% 
      dplyr::filter(
        time > T0,
        g8_i == 1
      ) %>% 
      dplyr::summarise(
        group = "8",
        att_pop_multiperiod =
          mean(unique(tau_t)) * scale_8 * mean_abs_tau_i,
        fraction_within_group =
          sum(z_it) / sum(df_design_multiperiod$z_it)
      )
  )

att_pop_multiperiod_group %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
att_pop_multiperiod <- 
  att_pop_multiperiod_group %>% 
  dplyr::summarise(
    att_pop_multiperiod =
      att_pop_multiperiod %*%
      fraction_within_group
  ) %>% 
  dplyr::pull(att_pop_multiperiod)

att_pop_multiperiod
```

```{r}
att_pop_multiperiod <- 
  att_pop_multiperiod_group$att_pop_multiperiod %*%
  att_pop_multiperiod_group$fraction_within_group

att_pop_multiperiod
```

```{r}
att_sample_multipleriod_group <- 
  df_design_multiperiod %>% 
    dplyr::filter(
      group_i > T0
    ) %>% 
    dplyr::group_by(
      group_i
    ) %>% 
    dplyr::summarise(
      tau_it = mean(tau_it)
    )

att_sample_multipleriod_group  
```

```{r}
att_sample_multipleriod <- 
  df_design_multiperiod %>% 
  dplyr::filter(
    z_it == 1
  ) %>% 
  dplyr::summarise(
    tau_it = mean(tau_it)
  ) %>% 
  dplyr::pull(tau_it)

att_sample_multipleriod
```

```{r}
df_design_observed <- 
  df_design %>% 
    dplyr::select(
      id,
      time,
      g_i,
      z_it,
      y_it
    )

head(df_design_observed) %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
df_design_observed %>% 
  dplyr::pull(g_i) %>% 
  mean()
```

```{r}
post <- 
  df_design_observed %>% 
    dplyr::filter(
      time > T0
    ) %>% 
    dplyr::summarise(
      y_it = 
        sum(y_it * g_i) / sum(g_i) - 
        sum(y_it * (1 - g_i)) / sum(1 - g_i)
    ) %>% 
    dplyr::pull(y_it)

post
```

```{r}
pre <- 
  df_design_observed %>% 
  dplyr::filter(
    time <= T0
  ) %>% 
  dplyr::summarise(
    y_it = 
      sum(y_it * g_i) / sum(g_i) -
      sum(y_it * (1 - g_i)) / sum(1 - g_i)
  ) %>% 
  dplyr::pull(y_it)

pre
```

```{r}
did <- post - pre
did
```

```{r}
lsdv <- 
  plm::plm(
    formula = y_it ~ z_it,
    data = df_design_observed,
    index = c(
      "id",
      "time"
    ),
    effect = "twoways"
  )

clubSandwich::coef_test(
  obj = lsdv,
  vcov = "CR1",
  cluster = "id",
  test = "naive-t"
) %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
estimatr::lm_robust(
  formula = y_it ~ z_it,
  data = df_design_observed,
  clusters = id,
  fixed_effects = id + time,
  se_type = "stata"
) %>% 
  summary() %>% 
  coefficients() %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
df_design_multiperiod_obserbed <- 
  df_design_multiperiod %>% 
  dplyr::select(
      "id",
      "time",
      "group_i",
      "g5_i",
      "g6_i",
      "g7_i",
      "g8_i",
      "z5_it",
      "z6_it",
      "z7_it",
      "z8_it",
      "z_it",
      "y_it"
  )

head(df_design_multiperiod_obserbed) %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
trend_control <- 
  tibble::tibble(
    group_i = c(5, 6, 7, 8),
    trend_control = 
      df_design_multiperiod_obserbed %>% 
      dplyr::filter(
        group_i == 0
      ) %>% 
      dplyr::summarise(
        group_5 =
          sum(y_it * (time >= 5)) /  sum(time >= 5) -
                sum(y_it * (time < 5)) / sum(time < 5),
        group_6 =
          sum(y_it * (time >= 6)) /  sum(time >= 6) -
                sum(y_it * (time < 6)) / sum(time < 6),
        group_7 =
          sum(y_it * (time >= 7)) /  sum(time >= 7) -
                sum(y_it * (time < 7)) / sum(time < 7),
        group_8 =
          sum(y_it * (time >= 8)) /  sum(time >= 8) -
                sum(y_it * (time < 8)) / sum(time < 8),
        ) %>% 
      t()
  )
```

```{r}
trend_treated <- 
      df_design_multiperiod_obserbed %>% 
      dplyr::filter(
        group_i > 0
      ) %>% 
      dplyr::group_by(
        group_i
      ) %>% 
      dplyr::summarise(
        trend_treated =
          sum(y_it * (time >= group_i)) / sum(time >= group_i) -
          sum(y_it * (time < group_i)) / sum(time < group_i),
        proporion =
          sum(z_it) / sum(df_design_multiperiod_obserbed$z_it)
  )
```

```{r}
df_did <- 
  dplyr::left_join(
    trend_control,
    trend_treated,
    by = "group_i"
  )

df_did <- 
  df_did %>% 
  dplyr::mutate(
    did_dif = trend_control - trend_treated
  ) %>% 
  dplyr::select(
    group_i,
    did_dif,
    proporion
  )

df_did <- 
  df_did %>% 
  dplyr::left_join(
    att_sample_multipleriod_group,
    by = "group_i"
  )

df_did %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
cbind(
  df_did %>% 
    dplyr::summarise(
      did_dif_average = 
        sum(did_dif * proporion)
    ),
  att_sample_multipleriod
)
```

\begin{align*}
 Y_{it} = \mu_i + \theta_t + \tau Z_{it} + \epsilon_{it}
\end{align*}

```{r}
lsdv <- 
  df_design_multiperiod_obserbed %>% 
  plm::plm(
    formula = y_it ~ z_it,
    data = .,
    index = c(
      "id",
      "time"
    ),
    effect = "twoways"
  )

clubSandwich::coef_test(
  obj = lsdv,
  vcov = "CR1",
  cluster = "id",
  test = "naive-t"
) %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
estimatr::lm_robust(
  formula = y_it ~ z_it,
  data = df_design_multiperiod_obserbed,
  clusters = id,
  fixed_effects = id + time,
  se_type = "CR0"
)
```

```{r}
result <- 
  bacondecomp::bacon(
    formula = y_it ~ z_it,
    data = df_design_multiperiod_obserbed,
    id_var = "id",
    time_var = "time"
  )
```

```{r}
result %>% 
  ggplot(
    aes(
      x = result$weight,
      y = result$estimate,
      colour = factor(result$type)
    )
  ) +
  geom_point() +
  labs(
    x = "Weight",
    y = "Estimate",
    color = "Type"
  ) +
  scale_color_viridis_d() +
  theme_classic() +
  theme(legend.position = "right")
```

\begin{align*}
 Y_{it} =& \beta + \sum_{k=5}^{8} \mu_k G_{ki} + 
\sum_{t'=2}^{T} \theta_{t'}1\{t = t'\} + \sum_{k=5}^{8} 
\sum_{t'=2}^{T} \tau_{kt'} G_{ki} 1\{t = t'\} + \epsilon_{it}
\end{align*}

```{r}
df_design_multiperiod_obserbed$z_it_t <- 
  df_design_multiperiod_obserbed$z_it * 
  df_design_multiperiod_obserbed$time +
  df_design_multiperiod_obserbed$z_it *
  df_design_multiperiod_obserbed$group_i * 100

df_design_multiperiod_obserbed <- 
  fastDummies::dummy_cols(
    .data = df_design_multiperiod_obserbed,
    select_columns = "z_it_t"
  )

df_design_multiperiod_obserbed <- 
  df_design_multiperiod_obserbed %>% 
  dplyr::select(
    -z_it_t_0
  )

fml <- as.formula(
  paste("y_it ~",
        paste(
          grep(
            "z_it_t_",
            names(df_design_multiperiod_obserbed),
            value = TRUE
          ),
          collapse = " + "
        ))
)

lsdv <- 
  plm::plm(
    formula = fml,
    data = df_design_multiperiod_obserbed,
    index = c(
      "id",
      "time"
    ),
    effect = "twoways"
  )

clubSandwich::coef_test(
  obj = lsdv,
  vcov = "CR1",
  test = "naive-t",
  cluster = "id"
) %>% 
  kbl() %>% 
  kable_styling()
```


```{r}
estimatr::lm_robust(
  formula = fml,
  data = df_design_multiperiod_obserbed,
  clusters = id,
  fixed_effects = id + time,
  se_type = "CR0"
) %>% 
  summary()
```

```{r}
df_compare <- 
  tibble::tibble(
    group_i = c(5, 6, 7, 8),
    did_lsdv = 
      c(
        mean(lsdv$coefficients[grep(
          "z_it_t_5",
          names(lsdv$coefficients),
          value = TRUE
        )]),
        mean(lsdv$coefficients[grep(
          "z_it_t_6",
          names(lsdv$coefficients),
          value = TRUE
        )]),
        mean(lsdv$coefficients[grep(
          "z_it_t_7",
          names(lsdv$coefficients),
          value = TRUE
        )]),
        mean(lsdv$coefficients[grep(
          "z_it_t_8",
          names(lsdv$coefficients),
          value = TRUE
        )])),
    did_dif = 
      trend_treated$trend_treated - trend_control$trend_control
  )

df_compare %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
df_compare$proportion <- 
  df_did$proporion

df_compare %>% 
  dplyr::summarise(
    did_lsdv_ave = sum(did_lsdv * proportion),
    did_dif_ave = sum(did_dif * proportion)
  ) %>% 
  kbl() %>% 
  kable_styling()
```

<br>

# [9-2]合成コントロール法

```{r}
data(
  "smoking",
  package = "tidysynth"
) 

smoking %>% 
  summary()

smoking %>% 
  head()
```

```{r}
year_start <- 1988
name_treated <- "California"
year_init <- min(smoking$year)
year_end <- max(smoking$year)
total_years <- year_end - year_init
```

```{r}
alpha0_retprice <- 35
alpha0_cigsale <- 140

delta_mean <- 0
delta_sd <- 2

mu_mean <- 0
mu_sd <- 2
```

```{r}
te_unif_lower <- 0.05
te_unif_upper <- 0.1
```

```{r}
eta_mean <- 0
eta_sd <- 3

rho <- 0.1
rho_zy <- 0.01
rho_zz <- 0.5
rho_yy <- 0.5
```

```{r}
window_income_age <- 1980:1988
window_beer <- 1984:1988
window_cigsale1 <- 1975
window_cigsale2 <- 1980
window_cigsale3 <- 1988

window_fit <- 1970:1988
```

```{r}
margin_ipop <- 0.02
sigf_ipop <- 7
bound_ipop <- 6
```

```{r}
set.seed(1)
```

```{r}
smoking_fake_factor_no_effect <- 
  smoking %>% 
    dplyr::group_by(
      state
    ) %>% 
    dplyr::mutate(
      mu_i_retprice =
        rnorm(
          n = 1,
          mean = mu_mean,
          sd = mu_sd
        ),
      mu_i_cigsale = 
        rnorm(
          n = 1,
          mean = mu_mean,
          sd = mu_sd
        )
    ) %>% 
    dplyr::ungroup() %>% 
    dplyr::group_by(
      year
    ) %>% 
    dplyr::mutate(
      retprice = 
        rnorm(
          n = 1,
          mean = delta_mean,
          sd = delta_sd
        ) +
        runif(
          n = 1
        ) * mu_i_retprice +
        rnorm(
          n = length(state)
        ),
      cigsale =
        alpha0_cigsale +
        rnorm(
          n = 1,
          mean = delta_mean,
          sd = delta_sd
        ) + 
        runif(
          n = 1
        ) * mu_i_cigsale +
        rnorm(
          n = length(state)
        )
    ) %>% 
    dplyr::ungroup() %>% 
    dplyr::select(
      -mu_i_retprice,
      -mu_i_cigsale
    ) 
```

```{r}
smoking_fake_factor_some_effect <- 
  smoking %>% 
  dplyr::group_by(
    state
  ) %>% 
  dplyr::mutate(
    mu_i_retprice = 
      rnorm(
        n = 1,
        mean = mu_mean,
        sd = mu_sd
      ),
    mu_i_cigsale =
      rnorm(
        n = 1,
        mean = mu_mean,
        sd = mu_sd
      )
  ) %>% 
  dplyr::ungroup() %>% 
  dplyr::group_by(
    year
  ) %>% 
  dplyr::mutate(
    retprice = 
      rnorm(
        n = 1,
        mean = delta_mean,
        sd = delta_sd
      ) +
      runif(
        n = 1
      ) * mu_i_retprice +
      rnorm(
        n = length (state)
      ),
    cigsale = 
      alpha0_cigsale +
      rnorm(
        n = 1,
        mean = delta_mean,
        sd = delta_sd
      ) +
      runif(
        n = 1
      ) * mu_i_cigsale +
      rnorm(
        n = length(state)
      )
  ) %>% 
  dplyr::ungroup() %>% 
  dplyr::select(
    -mu_i_retprice,
    -mu_i_cigsale
  ) %>% 
  dplyr::mutate(
    cigsale =
      ifelse(
        state == name_treated & year > year_start,
        cigsale * (
          1 -
            runif(
              n = 1,
              te_unif_lower,
              te_unif_upper
            )
        ),
        cigsale
      )
  )
```

\begin{align*}
Z_{it} =& \alpha_0^z + \rho_{zy} * \left(\frac{t - year\_start}{total\_yaers}\right)^2 Y_{it-1} + \rho_{zz} * \left(\frac{t - year\_init}{total\_years}\right)Z_{it-1} + \eta_{it}\\
Y_{it} =& \alpha_0^y + \rho Z_{it-1} + rho_{yy} * \left(\frac{t - year\_init}{tital\_years}\right)^2 Y_{it_i} + \eta_{it}
\end{align*}

```{r}
smoking_fake <- smoking
years <- unique(smoking_fake$year)

smoking_fake$retprice[smoking_fake$year == 1] <- 
  alpha0_retprice +
  rnorm(
    n = sum(smoking_fake$year == 1),
    mean = eta_mean,
    sd = eta_sd
  )

smoking_fake$cigsale[smoking_fake$year == 1] <- 
  alpha0_cigsale +
  rho *smoking_fake$retprice[smoking_fake$year == 1] +
  rnorm(
    n = sum(smoking_fake$year == 1),
    mean = eta_mean,
    sd = eta_sd
  )

for(
  t in years[2:length(years)]
) {
  smoking_fake$retprice[smoking_fake$year == t] <- 
    alpha0_retprice +
    rho_zy * (
      (t - (year_init + 10)) / total_years
    )^2 * smoking_fake$cigsale[smoking_fake$year == t- 1] +
    rho_zz * (
      (t - year_init) / total_years
    ) * smoking_fake$retprice[smoking_fake$year == t - 1] +
    rnorm(
      n = sum(smoking_fake$year == t),
      mean = eta_mean,
      sd = eta_sd
    )
  
  smoking_fake$cigsale[smoking_fake$year == t] <- 
    alpha0_cigsale +
    rho * smoking_fake$retprice[smoking_fake$year == t - 1] +
    rho_yy * (
      (t - year_init) / total_years
    )^2 * smoking_fake$cigsale[smoking_fake$year == t - 1] +
    rnorm(
      n = sum(smoking_fake$year == t),
      mean = eta_mean,
      sd = eta_sd
    )
}

smoking_fake_ar_no_effect <- smoking_fake
```

```{r}
smoking_fake <- smoking
years <- unique(smoking_fake$year)

smoking_fake$retprice[smoking_fake$year == 1] <- 
  alpha0_retprice +
  rnorm(
    n = sum(smoking_fake$year == 1),
    mean = eta_mean,
    sd = eta_sd
  )

smoking_fake$cigsale[smoking_fake$year == 1] <- 
  alpha0_cigsale +
  rho *smoking_fake$retprice[smoking_fake$year == 1] +
  rnorm(
    n = sum(smoking_fake$year == 1),
    mean = eta_mean,
    sd = eta_sd
  )

for(
  t in years[2:length(years)]
) {
  smoking_fake$retprice[smoking_fake$year == t] <- 
    alpha0_retprice +
    rho_zy * (
      (t - (year_init + 10)) / total_years
    )^2 * smoking_fake$cigsale[smoking_fake$year == t- 1] +
    rho_zz * (
      (t - year_init) / total_years
    ) * smoking_fake$retprice[smoking_fake$year == t - 1] +
    rnorm(
      n = sum(smoking_fake$year == t),
      mean = eta_mean,
      sd = eta_sd
    )
  
  smoking_fake$cigsale[smoking_fake$year == t] <- 
    alpha0_cigsale +
    rho * smoking_fake$retprice[smoking_fake$year == t - 1] +
    rho_yy * (
      (t - year_init) / total_years
    )^2 * smoking_fake$cigsale[smoking_fake$year == t - 1] +
    rnorm(
      n = sum(smoking_fake$year == t),
      mean = eta_mean,
      sd = eta_sd
    )
  
  smoking_fake$cigsale[smoking_fake$year == t &
                         smoking_fake$state == "California"] <- 
    smoking_fake$cigsale[smoking_fake$year == t &
                         smoking_fake$state == "California"] * (
                           1 - 
                             runif(
                               n = 1,
                               te_unif_lower,
                               te_unif_upper
                             ) * (
                               t > year_start
                             )
                         )
    
}

smoking_fake_ar_some_effect <- smoking_fake
```

```{r}
smoking_out_factor_noeffect <- 
  smoking_fake_factor_no_effect %>% 
  tidysynth::synthetic_control(
    outcome = cigsale,
    unit = state,
    time = year,
    i_unit = name_treated,
    i_time = year_start,
    generate_placebos = TRUE
  ) %>% 
  tidysynth::generate_predictor(
    time_window = window_income_age,
    ln_income = mean(lnincome, na.rm = TRUE),
    youth = mean(age15to24, na.rm = TRUE)
  ) %>% 
  tidysynth::generate_predictor(
    time_window = window_beer,
    beer_sales = mean(beer, na.rm = TRUE)
  ) %>% 
  tidysynth::generate_predictor(
    time_window = window_cigsale1,
    cigsale_1 = cigsale
  ) %>% 
  tidysynth::generate_predictor(
    time_window = window_cigsale2,
    cigsale_2 = cigsale
  ) %>% 
  tidysynth::generate_predictor(
    time_window = window_cigsale3,
    cigsale_3 = cigsale
  ) %>% 
  tidysynth::generate_weights(
    optimization_window = window_fit,
    margin_ipop = margin_ipop,
    sigf_ipop = sigf_ipop,
    bound_ipop = bound_ipop
  ) %>% 
  tidysynth::generate_control()
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::plot_trends()
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::plot_differences()
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::plot_weights()
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::grab_balance_table() %>% 
  kbl() %>% 
  kable_styling()
```

```{r}
smoking_fake_factor_no_effect
smoking
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::plot_placebos()
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::plot_placebos(
    prune = FALSE
  )
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::plot_mspe_ratio()
```

```{r}
smoking_out_factor_noeffect %>% 
  tidysynth::grab_significance() %>% 
  kbl() %>% 
  kable_styling()
```

```{r cache=TRUE}
smoking_out_factor_noeffect_check <- 
  call_synthetic_control(
    data = smoking_fake_factor_no_effect,
    name_treated = name_treated,
    year_start = year_start,
    window_income_age = window_income_age,
    window_beer = window_beer,
    window_cigsale1 = window_cigsale1,
    window_cigsale2 = window_cigsale2,
    window_cigsale3 = window_cigsale3,
    margin_ipop = margin_ipop,
    sigf_ipop = sigf_ipop,
    bound_ipop = bound_ipop
  )
```

```{r cache=TRUE}
smoking_out_some_effect <- 
  call_synthetic_control(
    data = smoking_fake_factor_some_effect,
    name_treated = name_treated,
    year_start = year_start,
    window_income_age = window_income_age,
    window_beer = window_beer,
    window_cigsale1 = window_cigsale1,
    window_cigsale2 = window_cigsale2,
    window_cigsale3 = window_cigsale3,
    margin_ipop = margin_ipop,
    sigf_ipop = sigf_ipop,
    bound_ipop = bound_ipop
  )
```

```{r}
smoking_out_some_effect %>% 
  tidysynth::plot_trends()
```

```{r}
smoking_out_some_effect %>% 
  tidysynth::plot_differences()
```


```{r}
smoking_out_some_effect %>% 
  tidysynth::plot_placebos()
```

```{r}
smoking_out_some_effect %>% 
  tidysynth::plot_mspe_ratio()
```

```{r}
smoking_out_some_effect %>% 
  tidysynth::grab_significance() %>% 
  kbl() %>% 
  kable_styling()
```

```{r cache=TRUE}
smoking_out_ar_noeffect <- 
  call_synthetic_control(
    data = smoking_fake_ar_no_effect,
    name_treated = name_treated,
    year_start = year_start,
    window_income_age = window_income_age,
    window_beer = window_beer,
    window_cigsale1 = window_cigsale1,
    window_cigsale2 = window_cigsale2,
    window_cigsale3 = window_cigsale3,
    margin_ipop = margin_ipop,
    sigf_ipop = sigf_ipop,
    bound_ipop = bound_ipop
  )
```

```{r}
smoking_out_ar_noeffect %>%  
  tidysynth::plot_trends()
```

```{r}
smoking_out_ar_noeffect %>% 
  tidysynth::plot_placebos()
```

```{r}
smoking_out_ar_noeffect %>% 
  tidysynth::plot_mspe_ratio()
```

```{r}
smoking_out_ar_noeffect %>% 
  tidysynth::grab_significance() %>% 
  kbl() %>% 
  kable_styling()
```

```{r cache=TRUE}
smoking_out_ar_some_effect <- 
  call_synthetic_control(
    data = smoking_fake_ar_some_effect,
    name_treated = name_treated,
    year_start = year_start,
    window_income_age = window_income_age,
    window_beer = window_beer,
    window_cigsale1 = window_cigsale1,
    window_cigsale2 = window_cigsale2,
    window_cigsale3 = window_cigsale3,
    margin_ipop = margin_ipop,
    sigf_ipop = sigf_ipop,
    bound_ipop = bound_ipop
  )
```

```{r}
smoking_out_ar_some_effect %>% 
  tidysynth::plot_trends()
```

```{r}
smoking_out_ar_some_effect %>% 
  tidysynth::plot_placebos()
```

```{r}
smoking_out_ar_some_effect %>% 
  tidysynth::plot_mspe_ratio()
```

```{r}
smoking_out_ar_some_effect %>% 
  tidysynth::grab_significance() %>% 
  kbl() %>% 
  kable_styling()
```

















